Sheafification in HoTT

### 2015-01-12 paper/sheaf_lics.tex
extend is_classical_IsTrunc to -2

\subsection{Definitions and first properties}
\label{sec:def}

@@

\subsection{Construction of sheafification}
\label{sec:sheafification}

@@

\subsubsection{For h-propositions}
\label{sec:h-propositions}

For the case $n=-1$, one can take any left exact modality on
$\HProp$. Here we took the $\lnot\lnot$ modality~:
$$\forall P:\HProp,~\modal P = \lnot\lnot P.$$
One can easily show that it defines a left exact modality.

\subsubsection{From Type to Separated Type}
\label{sec:from-type-separated}
In this section, we suppose given a truncation index $n\geqslant -1$,
and a left exact modality $\modal$ on $\Type_n$, compatible with the
modality on $\HProp$.

Let $T$ be in $\Type_{n+1}$. We define $\square T$ as the image of
$\modal^T \circ \{\cdot\}_T$, as in
$$\xymatrix{
  T \ar[r]^{\{\cdot\}_T} \ar[d]_{\mu_T} & \Type_n^T \ar[d]^{\modal^T} \\
  \square T \ar[r]& \left( \Type_n^\modal \right)^T
}, $$
where $\{\cdot\}_T$ is the singleton map $\lambda (t:T),~\lambda
(t':T),~t=t'$.
In type theory words, 
$$\square T = \im (\lambda~t:T,~\lambda~ t',~ \modal (t = t')).$$

@@

  Let $k:\nat$, let's show that 
\begin{align*}
  &\sum_{t:T^k} (\mu_T t_1 = \mu_T t_2 \land \cdots
    \land \mu_T t_{k-1} \\
  = &\mu_T t_k) = \sum_{t:T^k} \modal (t_1 = t_2 \land \cdots
  \land t_{k-1} = t_k)
\end{align*}
By induction on $k$, and the preservation of products by $\modal$, it
suffices to show that for all $a,b:T$, $\modal (a=b) = (\mu_T a =
\mu_T b)$, which is true by univalence.
If $U$ is a separated type, we can now easily define an inverse to
$\lambda\,(f:\square T \to f),~x \circ \mu_T$.
\end{proof}

\begin{itemize}

\item $(\square,~\mu)$ is a modality.

\end{itemize}

\subsubsection{From Separated Type to Sheaf}
\label{sec:separated-to-sheaf}

\begin{itemize}
\item 
\begin{thm}
  Any type $A:\Type_{n+1}$ closed in a sheaf is itself a sheaf.
\end{thm}

\item Definition of sheafification reflextive subuniverse
  $(\star,~\nu)$
\item left exactness
\item cumulativity
\end{itemize}

\section{Future Works}
\label{sec:future-works}

@@

>>>>

% \subsection{Definitions and first properties}
% \label{sec:def}

@@

\section{Construction of sheafification}
\label{sec:sheafification}

@@

\subsection{For h-propositions}
\label{ssec:h-propositions}

For the case $n=-1$, one can take any left exact modality on
$\HProp$. Here we took the $\lnot\lnot$ modality~:
$$\forall P:\HProp,~\modal_j P = \lnot\lnot P.$$
One can easily show that it defines a left exact modality.

\subsection{From Type to Separated Type}
\label{ssec:from-type-separated}
In this section, we suppose given a truncation index $n\geqslant -1$,
and a left exact modality $\modal$ on $\Type_n$, compatible with the
modality on $\HProp$.

Let $T$ be in $\Type_{n+1}$. We define $\square T$ as the image of
$\modal^T \circ \{\cdot\}_T$, as in
$$\xymatrix{
  T \ar[r]^{\{\cdot\}_T} \ar[d]_{\mu_T} & \Type_n^T \ar[d]^{\modal^T} \\
  \square T \ar[r]& \left( \Type_n^\modal \right)^T
}, $$
where $\{\cdot\}_T$ is the singleton map $\lambda (t:T),~\lambda
(t':T),~t=t'$.
In type theory words, 
\begin{align*}
\square T &= \im (\lambda~t:T,~\lambda~ t',~ \modal (t = t')) \\
          &= \sum_{u:T \to \Type_n^\modal} \left\| \sum_{a:X} 
            (\lambda t,~\modal (a=t)) = u\right\|
\end{align*}

@@

  Let $k:\nat$, let's show that 
\begin{align*}
  &\sum_{t:T^k} (\mu_T t_1 = \mu_T t_2 \land \cdots
    \land \mu_T t_{k-1} \\
  = &\mu_T t_k) = \sum_{t:T^k} \modal (t_1 = t_2 \land \cdots
  \land t_{k-1} = t_k)
\end{align*}
By induction on $k$, and the preservation of products by $\modal$, it
suffices to show that for all $a,b:T$, $\modal (a=b) = (\mu_T a =
\mu_T b)$, which is true by univalence.
\end{proof}

Now that $\square T$ is a colimit, we can easily define an inverse to
$\lambda\,(f:\square T \to U),~x \circ \mu_T$ for any separated type
$U$, using the universal property of the colimit.

We now have to prove point {\it (v)} in the definition of
modality. Let $A:\Type_{n+1}$ be a sheaf and $B:A \to \Type_{n+1}$ be
a sheaf family. We want to show that $\sum_{x:A} (Bx)$ is
separated. Let $E$ be a type, and $\sum_{e:E} (\chi\,e)$ a dense
subobject of E.

Let $f,g$ be two maps from $\sum_{e:E} (\chi\,e)$ to $\sum_{x:A}
(Bx)$, equal when precomposed with $\pi_1$.

As $A$ is separated, for any $x:E$, the first components of $f x$ and
$g x$ are equal. For the second components, notice that for all $x:E$,
$\sum_{y:E} x = y$ has a dense subobject, $\sum_{y:\sum_{e:E} (\chi\,
  e)} x=y_1$. 
Using the separation property with these type, one can show the second
components of $f x$ and $g x$ are equals too, with respect to the
first path.

\subsection{From Separated Type to Sheaf}
\label{ssec:separated-to-sheaf}

If $T$ is already a separated type, the following lemma alllows us
to build a sheaf~:
\begin{lem}
  Let $T:\Type_{n+1}$ be separated, and $U$ be a sheaf. If $T$ embeds
  in $U$, and is closed in $U$, then $T$ is a sheaf.
\end{lem}

As any separated type $T$ embeds in $\left(\Type_n^\modal\right)^T$,
it suffices to take the closure of $T$ to get a sheaf.

\subsection{Summary}
\label{ssec:summary}

If $T:\Type_{n+1}$, the sheafification of $T$ is
$$\star T = \sum_{u:T \to \Type_n^\modal} \lnot\lnot\left\| \sum_{a:X} 
            (\lambda t,~\modal (a=t)) = u\right\|$$

We already know that $\star$ defines a modality. It remains to show
that this modality is left exact.

The last thing to prove is the cumulativity of our sheafifications~:
\begin{prop}
  If $T:\Type_n$, then $\modal T = \star \widehat T$ (where $\widehat
  T$ is $T$ seen as a $\Type_{n+1}$.
\end{prop}
\section{Future Works}
\label{sec:future-works}

@@

Extend the sheafification to all types, even if non truncated.
